### 2024-06-14 conteudo/tool/architecture.tex
Add additional work of 14/06

Our proposed tool is a Command Line Interface (CLI) software, the tool purpose is to enable developers to query 
information about code clone duplication in a function level, by function level we mean to find functions in a codebase that 
are code duplications. The tool is separated in two steps. The 
first one, denoted as Setup, is executed only once for each codebase and it is responsible for processing the
codebase doing tasks such as extracting functions of the code files 
and searching for code clone duplications. The second step, denoted as Query Responder, is
responsible to execute the tool functionalities using the information obtained in the Setup step. More information about the 
Setup and Query Responder behavior can be found in \ref{subsec:architecture} and in \ref{subsec:func}.

@@

@@

\subsection{Tool functionalites}
\label{subsec:func}

>>>>

@@

The Function Parser receives the input codebase and transforms it into the temporary codebase. The Function Parser iterates through
every source code file from the programming language it support and use a specific programming languague's function 
extractor to extract
every function in the file, for each function extracted we create a new source code file and a metadata file in the temporary codebase
which is represented by the pair \textbf{<source code file, function extracted>}, which represents the source code file the 
function is extracted from and the 
proper function. The new source code file only contains the source code from the function it represents, while the metadata file 
contains extra relevant information such as function name, the line the function it began to be declared in the original souce code 
file and the line the function's body ends in the original source code file. The programming language we support at the moment 
is C and Java. Can be found a example of a transform of a source code in the (CRIAR UM APENDICE E COLOCAR AQUI).

About the programming languague's function extractor, we approached this problem in a way that any person comfortable with a language
can adapt our approach to their specific programming language. Usually, the code blocks can be easily extracted from 
source code files, independently if the code blocks are defined by curly brackets or by indentation, and it is possible to
infer if it represents a function's body given how deeply it is in the code context and a few lines before the start 
of the code block. We followed exactly this approach to implement the function extractor for the languagues we implemented. 
As a alternative approach, we can build the syntax tree \citep{compiler} of the programming language and use it to 
extract the functions, which is a more complex task then our main approach. For the programming languages we support, we implemented
it as follow:

\begin{itemize}
  \item \textbf{C}:
  \item \textbf{Java}:
\end{itemize}

@@

### 2024-06-14 conteudo/tool/tool.tex
Add additional work of 14/06

Our proposed tool is a Command Line Interface (CLI) software, the tool purpose is to enable developers to query 
information about code clone duplication in a function level. The tool is separated in two steps. the 
first one, denoted as Setup, is responsible for processing the codebase doing tasks such as extracting functions of the code files 
and searching for code clone duplications. The second step, denoted as Query Responder, is
responsible to execute the tool functionalities using the information obtained in the Setup step. More information about the 
Setup and Query Responder behavior can be found in \ref{subsec:architecture} and in \ref{subsec:func}.

\subsection{Tool architecture}
\label{subsec:architecture}

\subsection{Tool functionalites}
\label{subsec:func}

>>>>

Our proposed tool is a Command Line Interface (CLI) software, the tool purpose is to enable developers to query 
information about code clone duplication in a function level, by function level we mean to find functions in a codebase that 
are code duplications. The tool is separated in two steps. The 
first one, denoted as Setup, is executed only once for each codebase and it is responsible for processing the
codebase doing tasks such as extracting functions of the code files 
and searching for code clone duplications. The second step, denoted as Query Responder, is
responsible to execute the tool functionalities using the information obtained in the Setup step. More information about the 
Setup and Query Responder behavior can be found in \ref{subsec:architecture} and in \ref{subsec:func}.
